Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2023-05-12 doc/manuscript/ESSDmanuscript.Rmd
update through end of 6.1

In terms of variables transferred, records were sent for `r n_relevant_variables_records_sent` variables (or closely-related variable groups), including variables from each C pool (Table `r table_variables`).
The majority (`r round(n_records_sent_stocks/n_records_sent_to_EFDB, 2)*100`%) of records sent were for C stocks, including
`r round(n_records_sent_biomass/n_records_sent_to_EFDB,2)*100`% for total biomass, 
`r round(n_records_sent_agb/n_records_sent_to_EFDB,2)*100`% for aboveground biomass,
`r round(n_records_sent_agb_components/n_records_sent_to_EFDB,2)*100`% for components of aboveground biomass (wood or foliage), 
`r round(n_records_sent_rootbiomass/n_records_sent_to_EFDB,2)*100`% for root biomass, 
`r round(n_records_sent_rootbiomass_components/n_records_sent_to_EFDB,2)*100`% for components of root biomass (coarse or fine roots), 
`r round(n_records_sent_deadwood/n_records_sent_to_EFDB,2)*100`% for dead wood, 
`r round(n_records_sent_deadwood_components/n_records_sent_to_EFDB,2)*100`% for components of dead wood (standing or fallen), 
`r round(n_records_sent_litter/n_records_sent_to_EFDB,2)*100`% for litter (entire O horizon or OL layer component),
and `r round(n_records_sent_soil/n_records_sent_to_EFDB,2)*100`% for SOM/ SOC.
Increment records totaled `r round(n_records_sent_increments/n_records_sent_to_EFDB*100, 0)`% of records sent, all for aboveground biomass excepting `r n_records_sent_delta.litter` records for organic horizon increments.
The remaining (`r round(n_records_sent_fluxes/n_records_sent_to_EFDB*100, 0)`%) of records sent described fluxes,
all of which were either inputs or outputs to the aboveground biomass pool,
and a subset of which also described inputs to the dead wood or litter pool (Table `r table_variables`, Fig. `r fig_variable_mapping`).

@@

In addition to the large potential to expand EFDB using records already in ForC, there are innumerous published EFDB-relevant forest C data that are not currently included in ForC, with more being published on a nearly daily basis. 
Coverage of particular variables or regions could be vastly improved through systematic review of the literature.
Indeed, recent efforts have compiled large databases of relevant data from monoculture plantation forests [@bukoski_rates_2022], ... *others?  (SUSAN)*. 
Such reviews valuable for assessing the availability of published EFDB-relevant forest C records, versus those that require additional data collection and analysis.

>>>>

In terms of variables transferred, records were sent for `r n_relevant_variables_records_sent` variables (or closely-related variable groups), including variables from each C pool (Table `r table_variables`).
The majority (`r round(n_records_sent_stocks/n_records_sent_to_EFDB, 2)*100`%) of records sent were for C stocks, including
`r round(n_records_sent_biomass/n_records_sent_to_EFDB,2)*100`% for total biomass, 
`r round(n_records_sent_agb/n_records_sent_to_EFDB,2)*100`% for aboveground biomass,
`r round(n_records_sent_agb_components/n_records_sent_to_EFDB,2)*100`% for components of aboveground biomass (wood or foliage), 
`r round(n_records_sent_rootbiomass/n_records_sent_to_EFDB,2)*100`% for root biomass, 
`r round(n_records_sent_rootbiomass_components/n_records_sent_to_EFDB,2)*100`% for components of root biomass (coarse or fine roots), 
`r round(n_records_sent_deadwood/n_records_sent_to_EFDB,2)*100`% for dead wood, 
`r round(n_records_sent_deadwood_components/n_records_sent_to_EFDB,2)*100`% for components of dead wood (standing or fallen), 
`r round(n_records_sent_litter/n_records_sent_to_EFDB,2)*100`% for litter (entire O horizon or OL layer component),
and `r round(n_records_sent_soil/n_records_sent_to_EFDB,2)*100`% for SOM/ SOC.
Increment records totaled `r round(n_records_sent_increments/n_records_sent_to_EFDB*100, 0)`% of records sent, virtually all for aboveground biomass (excepting `r n_records_sent_delta.litter` records for delta.O.horizon).
The remaining `r round(n_records_sent_fluxes/n_records_sent_to_EFDB*100, 0)`% of records sent described fluxes, all of which were either inputs or outputs to the aboveground biomass pool, a subset of which also described inputs to the dead wood or litter pool (Table `r table_variables`, Fig. `r fig_variable_mapping`).

@@

In addition to the large potential to expand EFDB using records already in ForC, there are innumerous published EFDB-relevant forest C data that are not currently included in ForC, with more being published on a nearly daily basis. 
Coverage of particular variables or regions could be vastly improved through systematic review of the literature.
Indeed, recent efforts have compiled large databases of relevant data from monoculture plantation forests [@bukoski_rates_2022], ... *others?  (SUSAN)*. 
Beyond expanding collections of relevant forest C records, such reviews are valuable for assessing the availability of published records and identifying variables and regions that require additional data collection and analysis.

### 2023-05-12 doc/manuscript/ESSDmanuscript.tex
resolve rounding problem
#46
update through end of 6.1

In terms of variables transferred, records were sent for 19 variables
(or closely-related variable groups), including variables from each C
pool (Table 2). The majority (82\%) of records sent were for C stocks,
including 3\% for total biomass, 53\% for aboveground biomass, 4\% for
components of aboveground biomass (wood or foliage), 4\% for root
biomass, 2\% for components of root biomass (coarse or fine roots), 5\%
for dead wood, 3\% for components of dead wood (standing or fallen), 4\%
for litter (entire O horizon or OL layer component), and 4\% for SOM/
SOC. Increment records totaled 9\% of records sent, including 8.55\% for
aboveground biomass increments and 0.28\% for organic horizon
increments. The remaining (9\%) of records sent described fluxes, all of
which were either inputs or outputs to the aboveground biomass pool, and
a subset of which also described inputs to the dead wood or litter pool
(Table 2, Fig. 1).

@@

In addition to the large potential to expand EFDB using records already
in ForC, there are innumerous published EFDB-relevant forest C data that
are not currently included in ForC, with more being published on a
nearly daily basis. Coverage of particular variables or regions could be
vastly improved through systematic review of the literature. Indeed,
recent efforts have compiled large databases of relevant data from
monoculture plantation forests \citep{bukoski_rates_2022}, \ldots{}
\emph{others? (SUSAN)}. Such reviews valuable for assessing the
availability of published EFDB-relevant forest C records, versus those
that require additional data collection and analysis.

>>>>

In terms of variables transferred, records were sent for 19 variables
(or closely-related variable groups), including variables from each C
pool (Table 2). The majority (82\%) of records sent were for C stocks,
including 3\% for total biomass, 53\% for aboveground biomass, 4\% for
components of aboveground biomass (wood or foliage), 4\% for root
biomass, 2\% for components of root biomass (coarse or fine roots), 5\%
for dead wood, 3\% for components of dead wood (standing or fallen), 4\%
for litter (entire O horizon or OL layer component), and 4\% for SOM/
SOC. Increment records totaled 9\% of records sent, virtually all for
aboveground biomass (excepting 4 records for delta.O.horizon). The
remaining 9\% of records sent described fluxes, all of which were either
inputs or outputs to the aboveground biomass pool, a subset of which
also described inputs to the dead wood or litter pool (Table 2, Fig. 1).

@@

In addition to the large potential to expand EFDB using records already
in ForC, there are innumerous published EFDB-relevant forest C data that
are not currently included in ForC, with more being published on a
nearly daily basis. Coverage of particular variables or regions could be
vastly improved through systematic review of the literature. Indeed,
recent efforts have compiled large databases of relevant data from
monoculture plantation forests \citep{bukoski_rates_2022}, \ldots{}
\emph{others? (SUSAN)}. Beyond expanding collections of relevant forest
C records, such reviews are valuable for assessing the availability of
published records and identifying variables and regions that require
additional data collection and analysis.
